Lambda Calculus through Tropical Mathematics

### 2023-01-12 section6.tex
commit

\item $\Mod$ can be equipped with a differential operator defined, for $f:!M\to N$, by 
\begin{align}\label{eq:dermod}
\Der[f](\alpha)=
\bigvee\left\{
f(\beta\cup [x]) \ \Big \vert  \ 
\iota_{n}(\beta)\otimes \iota_{1}(x) \leq S(\alpha)
\right\}
\end{align}
where $\iota_{k}: M_{k}\to \prod_{i\in I}M_{i}$ is the injection morphism given by $\iota_{k}(x)( k)=x$ and $\iota_{k}(x)(i\neq k)=\infty$,
and $S: !(X\times Y)\to !X\otimes !Y$ is the Seely isomorphism \cite{}, 
satisfying all axioms (D1)-(D7) and (DCurry), see the Appendix.
\end{enumerate}

>>>>

\item $\Mod$ can be equipped with a differential operator defined, for $f:!M\to N$, by 
\begin{align}\label{eq:dermod}
\Der[f](\alpha)=
\bigvee\left\{
f(\beta\cup [x]) \ \Big \vert  \ 
\iota_{n}(\beta)\otimes \iota_{1}(x) \leq S(\alpha)
\right\}
\end{align}
where $\iota_{k}: M_{k}\to \prod_{i\in I}M_{i}$ is the injection morphism given by $\iota_{k}(x)( k)=x$ and $\iota_{k}(x)(i\neq k)=\infty$,
and $S: !(M\times N)\to !M\otimes !N$ is the Seely isomorphism \cite{}, 
satisfying all axioms (D1)-(D7) and (DCurry), see the Appendix.
\end{enumerate}
